Using numerical modelling to investigate temperature and wave exposure as drivers

### 2019-09-04 morphology_paper.Rmd
general house cleaning and output updated

---
title: Using numerical modelling to investigate temperature and wave exposure as drivers
  of macroalgal characteristics
author: "R. Coppin, C. Rautenbach, T. Ponton and A.J Smit"
fontsize: 10pt
output:
  pdf_document: default
  word_document:
    reference_docx: frontiers_template.docx
geometry: margin=1in
papersize: A4
tables: yes
bibliography: refs_morphology_paper.bib
---

>>>>

---
title: Using numerical modelling to investigate temperature and wave exposure as drivers
  of macroalgal characteristics
author: "R. Coppin, C. Rautenbach, T. Ponton and A.J Smit"
fontsize: 10pt
output:
  word_document:
    reference_docx: frontiers_template.docx
  pdf_document: default
geometry: margin=1in
papersize: A4
tables: yes
bibliography: refs_morphology_paper.bib
---
